Distributions

### 2022-01-06 Ch2_distributions/Ch2_Figures.Rmd
Changed labels for plot grid.

#cp.grid <- plot_grid(NULL, cp.ln, cp.wei, ncol = 3)

@@

pp.grid <- plot_grid(pp.gam, pp.ln, pp.wei, nrow = 1)

@@

np.grid <- plot_grid(np.gam, np.ln, np.wei, nrow = 1)

@@

cp.grid <- plot_grid(legend.grid, cp.ln, cp.wei, ncol = 3)

plot_grid(cp.grid, pp.grid, np.grid, nrow = 3)

>>>>

cp.grid <- plot_grid(cp.ln, cp.wei, ncol = 2, labels = c("A)", "B)"), label_size = 9)

@@

pp.grid <- plot_grid(pp.gam, pp.ln, pp.wei, nrow = 1, labels = c("C)", "D)", "E)"), label_size = 9)

@@

np.grid <- plot_grid(np.gam, np.ln, np.wei, nrow = 1, labels = c("F)", "G)", "H)"), label_size = 9)

@@

#cp.grid <- plot_grid(legend.grid, cp.ln, cp.wei, ncol = 3)
row1 <- plot_grid(legend.grid, cp.grid, ncol = 2, rel_widths = c(1,2))

plot_grid(row1, pp.grid, np.grid, nrow = 3)
